|

### 2022-12-08 paper_comparison/paper_comparison/paper_comparison.Rmd
clean code in 2.1

                 # Create a pseudo z to be able to use F-test
                 tmp_dat %>%
                   mutate(z = poly_model() %>%
                            {.$gen(n, computed = select(tmp_dat, x))} %>%
                            pull(z))
                 )$p_value,
               RESET3_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:3, 
                                                power_type = "fitted")$p_value,
               RESET4_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:4, 
                                                power_type = "fitted")$p_value,
               RESET5_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:5, 
                                                power_type = "fitted")$p_value,
               RESET6_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:6, 
                                                power_type = "fitted")$p_value,
               RESET7_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:7, 
                                                power_type = "fitted")$p_value,
               RESET8_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:8, 
                                                power_type = "fitted")$p_value,
               RESET9_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:9, 
                                                power_type = "fitted")$p_value,
               RESET10_p_value = POLY_MODEL$test(tmp_dat, 
                                                 test = "RESET", 
                                                 power = 2:10, 
                                                 power_type = "fitted")$p_value,
               BP_p_value = mod$test(tmp_dat)$p_value,
               SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
               boot_id = i)
        }) %>%
  reduce(bind_rows)
  }

@@

mod <- poly_model(include_z = FALSE, sigma = 0.25)
dat <- mod$gen(300)
patchwork::wrap_plots(
  mod$plot(dat, theme = theme_light()) +
    ggtitle("A. Good residuals") + 
    xlab("fitted values") + ylab("residuals"),
  mod$plot(mod$set_prm("include_z", TRUE)$gen(300, 
    computed = select(dat, x, e)), 
    theme = theme_light()) + 
    ggtitle("B. Non-linearity") +
    xlab("fitted values") + ylab("residuals"),
  mod$plot(heter_model(b = 64)$gen(300, 
    computed = select(dat, x, e)), 
    theme = theme_light()) + 
    ggtitle("C. Heteroskedasticity") +
    xlab("fitted values") + ylab("residuals"),
  mod$plot(heter_model(b = 0, 
    e = rand_lognormal(sigma = 0.5))$gen(300, 
    computed = select(dat, x)), 
    theme = theme_light()) + 
    ggtitle("D. Non-normality") +
    xlab("Fitted values") + ylab("Residuals")
)
```

>>>>

                 # Create a pseudo z to be able to use F-test
                 tmp_dat %>%
                   mutate(z = poly_model()$
                            gen(n, computed = select(tmp_dat, x)) %>%
                            pull(z))
                 )$p_value,
               RESET3_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:3, 
                                                power_type = "fitted")$p_value,
               RESET4_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:4, 
                                                power_type = "fitted")$p_value,
               RESET5_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:5, 
                                                power_type = "fitted")$p_value,
               RESET6_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:6, 
                                                power_type = "fitted")$p_value,
               RESET7_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:7, 
                                                power_type = "fitted")$p_value,
               RESET8_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:8, 
                                                power_type = "fitted")$p_value,
               RESET9_p_value = POLY_MODEL$test(tmp_dat, 
                                                test = "RESET", 
                                                power = 2:9, 
                                                power_type = "fitted")$p_value,
               RESET10_p_value = POLY_MODEL$test(tmp_dat, 
                                                 test = "RESET", 
                                                 power = 2:10, 
                                                 power_type = "fitted")$p_value,
               BP_p_value = mod$test(tmp_dat)$p_value,
               SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
               boot_id = i)
        }) %>%
  reduce(bind_rows)
  }

@@

# Base model
mod <- poly_model(include_z = FALSE, sigma = 0.25)

# Base data
dat <- mod$gen(300)

patchwork::wrap_plots(

  # Plot base data
  mod$plot(dat, theme = theme_light()) +
    ggtitle("A. Good residuals") + 
    xlab("fitted values") + 
    ylab("residuals"),

  # Include the z term
  # Reuse the x and e terms
  mod$plot(mod$
             set_prm("include_z", TRUE)$
             gen(300, computed = select(dat, x, e)), 
    theme = theme_light()) + 
    ggtitle("B. Non-linearity") +
    xlab("fitted values") + 
    ylab("residuals"),

  # Build a heter model
  # Reuse the x and e terms
  mod$plot(heter_model(b = 64)$
             gen(300, computed = select(dat, x, e)), 
    theme = theme_light()) + 
    ggtitle("C. Heteroskedasticity") +
    xlab("fitted values") + 
    ylab("residuals"),

  # Build a heter model with non-normal error
  # Reuse the x term
  mod$plot(heter_model(b = 0, e = rand_lognormal(sigma = 0.5))$
             gen(300, computed = select(dat, x)), 
    theme = theme_light()) + 
    ggtitle("D. Non-normality") +
    xlab("Fitted values") + 
    ylab("Residuals")
)
```
